Preliminary Data Analysis and Visualization

### 2023-07-27 Peliminary Data Analysis and Vizualization.Rmd
prelim visualizations

```{r}

cleaned_df %>%
  dplyr::filter(rep_acc == "accurate") %>%
  dplyr::group_by(timebins, speaker, subject) %>%
  dplyr::summarize(pupil_dilation = mean(pupil.binned, na.rm = T),
                   pupil_se = sd(pupil.binned, na.rm = T)/sqrt(n())) %>%
  ggplot() +
  aes(x = timebins,
      y = pupil_dilation,
      fill = speaker,
      color = speaker) +
  geom_ribbon(aes(ymin = pupil_dilation - pupil_se, ymax = pupil_dilation + pupil_se), alpha = .3) +
  geom_line() +
  coord_cartesian(xlim = c(0,3000)) +
  labs(x = "Time (ms)", y = "Pupil Dilation (arbitrary units)", fill = "Speaker", color = "Speaker") +
  theme_bw() + 
  facet_wrap("subject") +
  theme(legend.position = "bottom")

>>>>

```{r, message = F, warning = F}

cleaned_df %>%
  dplyr::filter(rep_acc == "accurate") %>%
  dplyr::group_by(timebins, speaker, subject) %>%
  dplyr::summarize(pupil_dilation = mean(pupil.binned, na.rm = T),
                   pupil_se = sd(pupil.binned, na.rm = T)/sqrt(n())) %>%
  ggplot() +
  aes(x = timebins,
      y = pupil_dilation,
      fill = speaker,
      color = speaker) +
  geom_ribbon(aes(ymin = pupil_dilation - pupil_se, ymax = pupil_dilation + pupil_se), alpha = .3) +
  geom_line() +
  coord_cartesian(xlim = c(0,3000)) +
  labs(x = "Time (ms)", y = "Pupil Dilation (arbitrary units)", fill = "Speaker", color = "Speaker") +
  theme_bw() + 
  facet_wrap("subject", ncol = 2) +
  theme(legend.position = "bottom")
